Scaling Automated Theory Exploration

### 2015-08-06 AI4FM/abstract.tex
Added hardlink to Bibtex.bib

Automated theory exploration has been applied to libraries in Isabelle
and Haskell, although we focus on the latter as its implementations are
the most mature (\textsc{Hipster} actually explores Isabelle by
translating code to Haskell first!). Haskell is interesting to target,
since its functional purity and algebraic structure make equational
properties common; recursion and higher-order functions make automation
non-trivial; and since these properties can't be expressed in Haskell
itself (without difficulty \cite{lindley2014hasochism}, at least), less
effort is spent discovering and proving these properties compared to
proof-oriented systems like Isabelle.

@@

\bibliographystyle{plain} \bibliography{/home/chris/Documents/ArchivedPapers/Bibtex}

>>>>

Automated theory exploration has been applied to libraries in Isabelle
and Haskell, although we focus on the latter as its implementations are
the most mature (demonstrated by \textsc{Hipster}, which explores Isabelle by
translating code to Haskell first). Haskell is interesting to target,
since its emphasis on pure functions and algebraic datatypes make it common for
functions to obey equational properties; although Haskell is not a theorem prover,
and hence cannot represent such equations . Also, the widespread use of
recursion and higher-order functions makes automated deduction non-trivial
effort is spent discovering and proving these properties compared to
proof-oriented systems like Isabelle.

@@

\bibliographystyle{plain} \bibliography{../Bibtex}
